\section*{Social Events}
\addcontentsline{toc}{section}{Social Events}

\subsection*{Welcome Cocktail \textemdash\ Monday, June 8, 2026}
\hypertarget{nav-cocktail}{}\label{nav-page-cocktail}

Kick off CASCA 2026 under the stars!

Join us on \textbf{Monday, June 8, 2026}, from \textbf{17:30 onwards} for our Welcome Cocktail at the \href{https://maps.app.goo.gl/HZDAgXDaX6Fj45Yd9}{\textbf{Montréal Planetarium} (4801 Pierre-de Coubertin Ave, Montréal, QC H1V 3V4)}.

Reconnect with colleagues, meet new collaborators, and enjoy an evening in one of Montréal's most iconic science venues. Thanks to the generous support of the Montréal Planetarium, attendees will have \textbf{exclusive access to the Planetarium's immersive exhibitions}, along with \textbf{complimentary broadcasts of its acclaimed multimedia astronomy shows} throughout the evening.

Whether you're exploring the cosmos beneath the dome, discussing the latest discoveries over refreshments, or simply enjoying the company of fellow astronomers, this promises to be a memorable start to the conference.

We warmly thank the Montréal Planetarium for sponsoring this special event.

\subsection*{Public Talk \textemdash\ Tuesday, June 9, 2026}
\hypertarget{nav-publictalk}{}\label{nav-page-publictalk}
Tuesday, June 9$^{\rm th}$, 2026 at 7pm, we will be hosting Nathalie N.-Q. Ouellette, Outreach Scientist for the James Webb Space Telescope in Canada. Join us to learn more about 'Galaxies en révolution: surprises du télescope Webb' and stay to observe the night sky alongside passionate amateur astronomers. 

\subsection*{Conference Banquet \textemdash\ Wednesday, June 10, 2026}
\hypertarget{nav-banquet}{}\label{nav-page-banquet}

The banquet will be held at \href{https://maps.app.goo.gl/Hh75s2zGi3QP911q9}{Espace Gare Viger, 735 rue Berri}, from 7\,pm to 10\,pm (19h00 to 22h00), a striking reception venue in Montréal's Old Port, less than a 10-minute walk from both Berri\textendash UQAM and Champ-de-Mars metro stations. Housed in the historic Château Viger (1898), the space blends old-world character (think grey stone, brick, and turreted ``Loire Valley château'' architecture) with a refined industrial elegance.

The evening will feature a buffet with multiple cuisine stations and desserts, encouraging you to move around and mingle! Water, sparkling water, and soft drinks will be provided to all, and alcoholic drinks will be available for purchase at the bar during the banquet at a cost of \$12.

